Charity analysis

### 2022-07-20 Shiny/Test/Flexdashboard rows.Rmd
Renaming value boxes.

### KPI
```{r}
valueBoxOutput("KPI_box")
```

### KPI 2
```{r}
valueBoxOutput("KPI_box2")
```

@@

  # Creating Fundraising ROI value -- transmute?
  KPI_fundraising_num <- reactive({
    exceldata() |>
      # most recent year
      filter(year == max(year)) |>
      transmute(
        # Calculating the value as a percentage; removing all other
        KPI_fundraising_num =
          (revenue_private_contributions +
            revenue_membership_fees - expenses_fundraising) /
            expenses_fundraising * 100
      ) |>
      # just want the single number
      pull()
  })

  # Creating the value box for administrative expenses
  output$KPI_box <- renderValueBox({
    valueBox(
      value = KPI_admin(),
      caption = "Admin spend",
      color = met.brewer("Troy", n = 1),
      icon = "fa-random"
    )
  })

  # Creating value box for fundraising ROI
  # Unsure about colour levels
  output$KPI_box2 <- renderValueBox({
    valueBox(
      # shortening(lengthening) the value with format()
      # Using str_c() to concatenate value and % sign;
      value = str_c(format(KPI_fundraising_num(), digits = 3), "%"),
      caption = "Fundraising ROI",

>>>>

### KPI
```{r}
valueBoxOutput("KPI_box_admin")
```

### KPI 2
```{r}
valueBoxOutput("KPI_box_fundraising")
```

@@

  # Creating Fundraising ROI value
  KPI_fundraising_num <- reactive({
    exceldata() |>
      # most recent year
      filter(year == max(year)) |>
      transmute(
        # Calculating the value as a percentage; removing all other
        KPI_fundraising_num =
          (revenue_private_contributions +
            revenue_membership_fees - expenses_fundraising) /
            expenses_fundraising * 100
      ) |>
      # just want the single number
      pull()
  })

  # Creating the value box for administrative expenses
  output$KPI_box_admin <- renderValueBox({
    valueBox(
      value = KPI_admin(),
      caption = "Admin spend",
      color = met.brewer("Troy", n = 1),
      icon = "fa-random"
    )
  })

  # Creating value box for fundraising ROI
  # Unsure about colour levels
  output$KPI_box_fundraising <- renderValueBox({
    valueBox(
      # shortening(lengthening) the value with format()
      # Using str_c() to concatenate value and % sign;
      value = str_c(format(KPI_fundraising_num(), digits = 3), "%"),
      caption = "Fundraising ROI",
